Effects of Reynolds Number on the Performance and Near-Wake Dynamics of a Vertical-Axis Cross-Flow Turbine

### 2015-04-21 paper.tex
Update figure caption for turbine drawing
Add turbine drawing
Add 'Dynamics' to title
Update bibfile and add citation for figshare repo

% Full title of the paper (Capitalized)
\Title{Effects of Reynolds Number on the Performance and Near-Wake of a
Vertical-Axis Cross-Flow Turbine}

@@

\begin{figure}[ht!]
\caption{Drawing of the turbine model. Note that the upper and lower mounting
flanges have been excluded as these were included in the tare drag
measurements.} 
\label{fig:turbine}
\end{figure}

@@

\todo[inline]{Cite reduced data and processing code on figshare.}

>>>>

% Full title of the paper (Capitalized)
\Title{Effects of Reynolds Number on the Performance and Near-Wake Dynamics of a
Vertical-Axis Cross-Flow Turbine}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.4\textwidth]{figures/turbine}
\caption{Turbine model drawing. Note that the upper and lower mounting
flanges have been excluded as these were included in the tare drag
measurements.} 
\label{fig:turbine}
\end{figure}

@@

The experimental data and processing/plotting code are available from
\cite{Bachant2015-RVAT-Re-dep-data}.
